SDSS-IV MaNGA: Radial Profiles of Specific Star Formation Rate in Nearby Interacting Galaxies

### 2020-06-05 maintex.tex
added discussion and conclusion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}\label{sec:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_unsplit.pdf}
\caption[]{\textbf{Left:} The individual difference profiles are shown in light grey while the stacked profile for the whole pair sample is shown in red. The highlighted region about the profile is the standard error of the mean of the stacked profile. \textbf{Right:} A histogram of the $\delta$log(sSFR) within the inner 0.5 \reff\ of the individual difference profiles. The red line shows the median value of the $\Delta$log(sSFR) enhancement, $\sim$0.25 dex.}
\label{fig:ssfr_all}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_full.pdf}
\caption[]{The $\Delta$log(sSFR) split into separate stellar mass bins. The left column gives the stacked difference profiles. The highlighted region about the profiles represents the standard error of the mean of the profile. The black dashed line represents the stacked profile of the full pair sample. The right column gives the nuclear $\Delta$log(sSFR) values. The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars). The vertical error bars on the black squares represent the standard deviation within the bin. The horizontal, dashed black lines represent the median central enhancement of the full pair sample. The top row shows the paired galaxies split by total stellar mass, the middle panel shows the paired galaxies split by mass ratio, and the bottom panel shows the paired galaxies split by projected separation. }
\label{fig:ssfr_full}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

@@

\hbox{}\clearpage

\appendix

\section{Figures}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/Mi-z.pdf}
\caption[The luminosity - redshift distribution and mass - redshift distribution of the MaNGA sample.]{On the left is the luminosity - redshift distribution of the MaNGA sample. The figure illustrates the unique distribution of the MaNGA sample. On the right, I replace the luminosity with stellar mass from the NSA catalog.}
\label{fig:Mi-z}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/pair_collage.pdf}
\caption[A collage of a subset of the inside-IFU pairs.]{A collage of a subset of the inside-IFU pairs. Each panel contains a 40$^{\arcsec}$ cutout of the SDSS pseudocolor image for the galaxy pair. The minor ticks on each panel's axis represents 2$^{\arcsec}$. The green squares highlight the identified galaxy pairs. }
\label{fig:collage}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=3in]{fig/mag_comp.pdf}
\caption[The comparison between the r-band magnitudes in Simard+11 and NSA catalog]{The comparison between the S\'ersic r-band apparent magnitude in \citet{Simard:2011} and the Elliptical Petrosian r-band apparent magnitude. The grey circles represent galaxies in the control sample, the blue squares represent galaxies in the outside-IFU sample, and the red diamonds represent the galaxies in the inside-IFU sample. Regardless of the sample, all of the galaxies covered by both of the catalogs have a similar apparent magnitude calculated from either sample.}
\label{fig:mag_comp}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/8485-3704.pdf}
\caption[Example of bootstrapping to quantify the deviation of the random subsample of controls]{An example of the bootstrapping used to quantify the errors associated with the random selection of the control subsample. From left to right, the first four panels show the individual dex profiles after a random sub-selection in grey. The random sub-selection is run 1000 times and the median profile after the 1000 cycles is given by the colored profile. The highlighted region about the colored profiles is the standard error of the mean of the median profile. From left to right each panel shows the random selection for a different number of controls to select; 5, 10, 20, and 50 controls. The panel on the right end shows the median profiles of all of the preceding panels. }
\label{fig:bootstrap}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}\label{sec:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_unsplit.pdf}
\caption[]{\textbf{Left:} The individual difference profiles are shown in light grey while the stacked profile for the whole pair sample is shown in red. The highlighted region about the profile is the standard error of the mean of the stacked profile. \textbf{Right:} A histogram of the $\delta$log(sSFR) within the inner 0.5 \reff\ of the individual difference profiles. The red line shows the median value of the $\Delta$log(sSFR) enhancement, $\sim$0.25 dex.}
\label{fig:ssfr_all}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/ssfr_full.pdf}
\caption[]{The $\Delta$log(sSFR) split into separate stellar mass bins. The left column gives the stacked difference profiles. The highlighted region about the profiles represents the standard error of the mean of the profile. The black dashed line represents the stacked profile of the full pair sample. The right column gives the nuclear $\Delta$log(sSFR) values. The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars). The vertical error bars on the black squares represent the standard deviation within the bin. The horizontal, dashed black lines represent the median central enhancement of the full pair sample. The top row shows the paired galaxies split by total stellar mass, the middle panel shows the paired galaxies split by mass ratio, and the bottom panel shows the paired galaxies split by projected separation. }
\label{fig:ssfr_full}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

% Nuclear comp with prev works
The enhancement to the sSFR in the centers of the whole pair sample is consistent with previous galaxy merger studies \citet{Ellison:2008, Barrera-Ballesteros:2015, Pan:2019}.

Different IFS studies have found different sSFR offsets in the disks of the paired galaxies. \citet{Barrera-Ballesteros:2015} found that the sSFR (using \ewha\ as a proxy) is suppressed in the disks of paired galaxies by $\sim$-0.13 dex. In contrast, \citet{Pan:2019} found that the sSFR is enhanced by 0.15 dex. In this work, we see that  $\Delta$log(sSFR) is roughly zero but leans towards being suppressed, $\Delta$log(sSFR) $=$ -0.1$-$0.0 dex.

In previous studies it was noted that the enhancement to the SFR is strongest in galaxy pairs with small mass ratios \citet{Ellison:2008}. We see the same effect; however, we have also shown that galaxy pairs with large mass ratios still show a substantial level of sSFR enhancement. Further, within these galaxy pairs with wide mass ratios we see that the less massive galaxy in the pair shows higher levels of sSFR enhancement. This implies that satellite galaxies are more affected by interaction induced star formation than the central galaxy.

 We saw that the $\Delta$log(sSFR) enhancement increases with closer projected separations \citet{Ellison:2008, Scudder:2012, Patton:2013}. This is unsurprising as nearby galaxy pairs will have just completed a close interaction. This enhancement persists out to wide separations where galaxy pairs separated by 50 kpc still show a substantial enhancement to the sSFR. \citet{Patton:2013} showed that the central enhancements to sSFR persists out to 150 kpc.

The closest pairs in our sample, pairs closer than 5 kpc, show no enhancement to the sSFR. This seems odd as one would think that these galaxies should show the strongest enhancements. The first thing to consider is that the sample contains no post-merger galaxies so we will not see the second large burst of star formation when the two galaxies are coalescing. The closest paired galaxies will either be pairs which are about to go through their first pericenter or galaxies which have just passed their first pericenter. In the galaxies which have passed their first pericenter, we believe that the timescale is still too small for the interaction induced gas inflows to travel from the galaxy's disk to its nucleus. Since the gas inflows haven't impacted the galaxy's nucleus, no enhancements to the sSFR will be seen. \citet{Scudder:2012} also found a delay in the burst of merger induced star formation in their hydrodynamical simulations.

@@

We studied a sample of paired, star forming galaxies using the MaNGA IFS survey. We have made a sample of 913 paired galaxies of which 202 are SFGs. We compared the radial profiles of the paired galaxies with 1862 isolated MaNGA SFGs. We found the following;

\begin{enumerate}
\item The sSFR is centrally enhanced within the inner 1.0 \reff\ by 0.25 $\pm$ 0.1 dex. 
\item The disks of the paired galaxies, R/\reff\ $=$ 1.0$-$2.5, show no signs of either sSFR enhancement or sSFR suppression. 
\item The sSFR enhancement in paired galaxies is independent of the total stellar mass of the paired galaxies, Massive galaxies experience the same level of sSFR enhancement as low mass galaxies.
\item The sSFR enhancement in paired galaxies does depend on the ratio between the masses of the paired galaxies. Galaxies with small mass ratios, $|\Delta$log(M)$|$ $=$ 0.0$-$0.5, see an enhancement to sSFR of 0.4 $\pm$ 0.1 dex, which is 0.15 dex higher than the average paired galaxies in the survey. We have also showed that paired galaxies with large mass ratios, 1.0 $<$ $|\Delta$log(M)$|$ $<$ 2.0, still show substantial levels of enhancement to the sSFR, 0.1$-$0.2 dex. 
\item Further, in paired galaxies with large mass ratios, the less massive galaxies experience higher levels of sSFR enhancement than the more massive galaxy in the pair, $\sim$0.1 dex.
\item The sSFR enhancement increases with closer projected separations where galaxies within 5$-$10 kpc have their sSFR enhanced by 0.5 $\pm$ 0.1 dex. The galaxies within 5 kpc experience no central enhancement to their sSFR. We believe that these galaxies have just passed their first pericenter and the merger induced gas-inflow have yet to reach the centers of these galaxies.
\item The paired galaxies will experience a faster mass growth rate of secular evolution of 1.6$-$2.3$\times$. The growth rate is highest for massive galaxies; however, the the low mass galaxies will see the stellar mass in their center more substantially increased over a 1 Gyr timescale.

\end{enumerate}

@@

%\hbox{}\clearpage

%\appendix

%\section{Figures}

@@
